\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in \proglang{R}

### 2014-01-23 papers/jss/article.Rnw
Improve the text about serializing messages.  Don't start the section with "However".
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@836 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

However, the main focus of Protocol Buffer messages is
efficiency. Therefore, messages are transported as a sequence
of bytes. The \texttt{serialize} method is implemented for
Protocol Buffer messages to serialize a message into a sequence of
bytes that represents the message.
%(raw vector in \proglang{R} speech) that represents the message.

>>>>

One of the primary benefits of Protocol Buffers is the efficient
binary wire-format representation.  
The \texttt{serialize} method is implemented for
Protocol Buffer messages to serialize a message into a sequence of
bytes (raw vector) that represents the message.
The raw bytes can then be parsed back into the original message safely
as long as the message type is known and its descriptor is available.
